|

### 2020-06-19 appendix/appendix.Rmd
fix appedix 06/19

## Aggregation Level

The aggregation level is also an important characteristic of the empirical tests of the _law of 1/n_. While the original model was built to explain the dynamics of majoritarian countries, the theory has been tested at the municipal, county, states, and country levels. In our sample, `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[1])` analysed data from the *local* level (municipalities and counties), `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[2])` studied the *state* (or Provincial) level, and `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[3])` used *country* level data.

```{r, fig.width=4, fig.height=3, fig.cap="Sample Aggregate Level", cache=TRUE}
dat %>%
  select(id, agglevel) %>%
  unique() %>%
  ggplot(aes(x=as.factor(agglevel))) +
    geom_bar(color = "black") +
  labs(x = "Sample Aggregate Level",
       y = "") +
  theme_bw()
```

@@

```{r, warning=F,message=F, cache=TRUE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method, agglevel) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method,
         `Sampling Aggregation Level` = agglevel)

@@

```{r, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method+agglevel,
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)

mod1 <- tibble(
     ` ` = c("Intercept",
             "Indepvar: N",
             "Indepvar: logN",
             "Year",
             "Published: No",
             "Elecsys: Non-Majoritarian",
             "Method: Panel",
             "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))
```

@@

mod1_permu <- tibble(
     ` ` = c("Intercept",
             "Indepvar: N",
             "Indepvar: logN",
             "Year",
             "Published: No",
             "Elecsys: Non-Majoritarian",
             "Method: Panel",
             "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

1. Compared with `K`, models with `N` and `logN` find significantly negative coefficients.
2. Year has null effect.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
5. In terms of modelling, passing from `OLS` to `PANEL` increases the detected effects.
6. When passing from `Local` to `State` or `Country` levels, it decreases the detected effect size.

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel,
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)

mod2 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Indepvar: logN",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod2_permu <- tibble(
     ` ` = c("Intercept",
             "Indepvar: N",
             "Indepvar: logN",
             "Year",
             "Published: No",
             "Elecsys: Non-Majoritarian",
             "Method: Panel",
             "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

1. Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
2. Year has a positive effect: the younger the publication, the higher the detected coefficient.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian` significantly decreases the effects found in our models.
5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
6. Passing from `Local` to `State` or `World` levels decreases the detected effect size.

@@

```{r, error=F, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method+agglevel,
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear)

mod3 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV",
          "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod3_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV",
          "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has null effect.
3. `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
4. In terms of the modeling, passing from `OLS` to `PANEL` or `IV` increases the detected effects.
5. When passing from `Local` to `State` level, the detected effects decrease.

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel,
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)

mod4 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV" ,
          "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod4_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV",
          "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method+agglevel,
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)

mod5 <- tibble(
   ` ` = c("Intercept",
           "Indepvar: N",
           "Year",
           "Published: No",
           "Method: Panel",
           "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod5_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Method: Panel",
          "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel,
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)

mod6 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Method: Panel",
          "Method: RDD",
          "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod6_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Method: Panel",
          "Method: RDD",
          "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, warning=F, error=F, message=F, cache=T}
coefs <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Indepvar: logN",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV",
          "Method: RDD",
          "AggLevel: States"))

aux = list(mod3, mod5, mod1) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model))
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order)) %>%
  filter(` ` != "Method: RDD") %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*",
                                     ifelse(. >= 0.05, " ",
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~(ifelse(is.na(.), " ", .)))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4, mod6, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model))
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order)) %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*",
                                     ifelse(. >= 0.05, " ",
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

@@

```{r, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel,
              test = "knha")
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel,
              test = "knha")
```

>>>>

@@

```{r, warning=F,message=F, cache=TRUE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method)

@@

```{r, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)

mod1 <- tibble(
     ` ` = c("Intercept",
             "Indepvar: N",
             "Indepvar: logN",
             "Year",
             "Published: No",
             "Elecsys: Non-Majoritarian",
             "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))
```

@@

mod1_permu <- tibble(
     ` ` = c("Intercept",
             "Indepvar: N",
             "Indepvar: logN",
             "Year",
             "Published: No",
             "Elecsys: Non-Majoritarian",
             "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

1. Compared with `K`, models with `N` and `logN` find significantly negative coefficients.
2. Year has null effect.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
5. In terms of modelling, passing from `OLS` to `PANEL` increases the detected effects.
6. When passing from `Country` to `Cross-Country`, it has no effect on the estimated coefficients.

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)

mod2 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Indepvar: logN",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod2_permu <- tibble(
     ` ` = c("Intercept",
             "Indepvar: N",
             "Indepvar: logN",
             "Year",
             "Published: No",
             "Elecsys: Non-Majoritarian",
             "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

1. Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
2. Year has a positive effect: the younger the publication, the higher the detected coefficient.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian` significantly decreases the effects found in our models.
5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.

@@

```{r, error=F, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear,
            control=list(maxiter=1000))

mod3 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod3_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has null effect.
3. `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
4. In terms of the modeling, passing from `OLS` to `PANEL` or `IV` increases the detected effects.

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)

mod4 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod4_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)

mod5 <- tibble(
   ` ` = c("Intercept",
           "Indepvar: N",
           "Year",
           "Published: No",
           "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod5_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)

mod6 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Method: Panel",
          "Method: RDD"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod6_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Method: Panel",
          "Method: RDD"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, warning=F, error=F, message=F, cache=T}
coefs <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Indepvar: logN",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV",
          "Method: RDD"))

aux = list(mod3, mod5, mod1) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model))
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order)) %>%
  filter(` ` != "Method: RDD") %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*",
                                     ifelse(. >= 0.05, " ",
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~(ifelse(is.na(.), " ", .)))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4, mod6, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model))
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order)) %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*",
                                     ifelse(. >= 0.05, " ",
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

@@

```{r, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method,
              test = "knha")
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method,
              test = "knha")
```
